Embedding Dimension of Polyhedral Losses

### 2020-01-28 colt-20/embed-dim.tex
Fixing tex errors
Added beginning of matrix rank proof sketch

  In general, observe that $x^{12}_1$ and $x^{13}_1$ must both be on the line $\inprod{v_1}{x} = -1$. \jessie{More detail}  
  Therefore, our three cases proceed as follows: $(i.) \|x^{13}_1\| > \|x^{12}_1\|$, $(ii.) \|x^{13}_1\| = \|x^{12}_1\|$, and $(iii.) \|x^{12}_1\| > \|x^{13}_1\|$.
  As the labels on normals $v_2$ and $v_3$ (and therefore, the respective witnesses), it suffices to just show cases $(i.)$ and $(ii.)$.

  \begin{enumerate}
  \item [$(i.)$] First, suppose $\|x^{13}_1\| < \|x^{12}_1\|$.
  This in turn implies that $\|v_3\| > \|v_2\|$ since both witnesses are on the line $\inprod{v_1}{x^{1i}_1} = -1$.
  Consider that in order for $x^{12}_1 \in F_1$, we must have both $\inprod{v_2}{x^{12}_1} = 1$ and $\inprod{v_3}{x^{12}_1} \leq 1$.
    \begin{align*}
    \inprod{v_2}{x^{12}_1}} = 1 &\iff \|v_2\| \cos(\theta(v_2, x^{12}_1)) = \frac 1 {\|x^{12}_2\|}\\
    \inprod{v_3}{x^{12}_1}} \leq 1 &\iff \|v_3\| \cos(\theta(v_3, x^{12}_1)) \leq \frac 1 {\|x^{12}_2\|}\\
\implies \|v_3\| \cos(\theta(v_3, x^{12}_1)) &\leq \|v_2\| \cos(\theta(v_2, x^{12}_1))\\
\implies 1 < \frac{\|v_3\|}{\|v_2\|} &\leq \frac{\cos(\theta(v_2, x^{12}_1))}{\cos(\theta(v_3, x^{12}_1))}\\
\implies \theta(v_3, x^{12}_1) &> \theta(v_2, x^{12}_1)\\
\implies \theta_{13} < \theta_{12}
    \end{align*}
    This yields a contradiction, as we must have $\theta_{12} < \theta_{13}$ in order to have $\inprod{v_3}{x^{13}_1} = \inprod{v_2}{x^{12}_1} = 1$.
    Therefore, we conclude that we cannot have $\|x^{12}_1\| > \|x^{13}\|$.
  	\item [$(ii.)$] Suppose that we have $\|x^{12}_1\| = \|x^{13}_1\|$.
  	As both witnesses are on the same halfspace $\{x : \inprod{v_1}{x} = -1\}$, we must have $x^{12}_1 = x^{13}_1$.

@@

\end{proof}

>>>>

  In general, observe that $x^{12}_1$ and $x^{13}_1$ must both be on the line $\inprod{v_1}{x} = -1$. \jessie{More detail}  
  Therefore, our three cases proceed as follows: $(i.) \|x^{13}_1\| > \|x^{12}_1\|$, $(ii.) \|x^{13}_1\| = \|x^{12}_1\|$, and $(iii.) \|x^{12}_1\| > \|x^{13}_1\|$.
  As the labels on normals $v_2$ and $v_3$ (and therefore, the respective witnesses) are arbitrary, it suffices to just show cases $(i.)$ and $(ii.)$.

  \begin{enumerate}
  \item [$(i.)$] First, suppose $\|x^{13}_1\| < \|x^{12}_1\|$.
  This in turn implies that $\|v_3\| > \|v_2\|$ since both witnesses are on the line $\inprod{v_1}{x^{1i}_1} = -1$.
  Consider that in order for $x^{12}_1 \in F_1$, we must have both $\inprod{v_2}{x^{12}_1} = 1$ and $\inprod{v_3}{x^{12}_1} \leq 1$.
    \begin{align*}
    \inprod{v_2}{x^{12}_1} = 1 &\iff \|v_2\| \cos(\theta(v_2, x^{12}_1)) = \frac 1 {\|x^{12}_2\|}\\
    \inprod{v_3}{x^{12}_1} \leq 1 &\iff \|v_3\| \cos(\theta(v_3, x^{12}_1)) \leq \frac 1 {\|x^{12}_2\|}\\
\implies \|v_3\| \cos(\theta(v_3, x^{12}_1)) &\leq \|v_2\| \cos(\theta(v_2, x^{12}_1))\\
\implies 1 < \frac{\|v_3\|}{\|v_2\|} &\leq \frac{\cos(\theta(v_2, x^{12}_1))}{\cos(\theta(v_3, x^{12}_1))}\\
\implies \theta(v_3, x^{12}_1) &> \theta(v_2, x^{12}_1)\\
\implies \theta_{13} < \theta_{12}
    \end{align*}
    This yields a contradiction, as we must have $\theta_{12} < \theta_{13}$ in order to have $\inprod{v_3}{x^{13}_1} = \inprod{v_2}{x^{12}_1} = 1$.
    Therefore, we conclude that we cannot have $\|x^{12}_1\| > \|x^{13}\|$.
  	\item [$(ii.)$] Suppose that we have $\|x^{12}_1\| = \|x^{13}_1\|$.
  	As both witnesses are on the same halfspace $\{x : \inprod{v_1}{x} = -1\}$, we must have $x^{12}_1 = x^{13}_1$.

@@

\end{proof}
\begin{proof}[Matrix rank proof]
  We can understand the QFP given in Section~\ref{sec:d-dim} for $\abstain{1/2}$ as a matrix rank problem.
  \jessie{Fill in explanation}

  With $n=4$, we observe the following matrix rank problem:
  \[
  \begin{bmatrix}
  	-1 & -1 & -1 & \cdot & \cdot & \cdot \\
  	1 & \cdot & \cdot & -1 & -1 & \cdot \\
  	\cdot & 1 & \cdot & 1 & \cdot & -1 \\
  	\cdot & \cdot & 1 & \cdot & 1 & 1 \\
  \end{bmatrix}
  \]

  Since this matrix is a submatrix of the matrix rank problem for $n=5$, any solution of this above problem must also be a solution in the large matrix given below.

  \[
  \begin{bmatrix}
  {\color{red} -1} & {\color{red} -1} & {\color{red} -1} & {\color{red} \cdot} & {\color{red} \cdot} & {\color{red} \cdot} & -1 & \cdot & \cdot & \cdot \\
  {\color{red} 1} & {\color{red} \cdot} & {\color{red} \cdot} & {\color{red} -1} & {\color{red} -1} & {\color{red} \cdot} & \cdot & -1 & \cdot & \cdot \\
  {\color{red} \cdot} & {\color{red} 1} & {\color{red} \cdot} & {\color{red} 1} & {\color{red} \cdot} & {\color{red} -1} & \cdot & \cdot & -1 & \cdot \\
  {\color{red} \cdot} & {\color{red} \cdot} & {\color{red} 1} & {\color{red} \cdot} & {\color{red} 1} & {\color{red} 1} & \cdot & \cdot & \cdot & -1 \\
  \cdot & \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & 1 & 1\\
  \end{bmatrix}
  \]

  In characterizing the solutions to the smaller matrix rank problem, let us establish the linear equality of the first two rows and second two rows.
  (Note that any combination of row pairs works without loss of generality.)
  The first column containing $[-1 \; 1]^T$ implies that we must have the two rows being the negation of each other, and similarly for the third and fourth rows with the final column.
  This gives a matrix of rank 2 as follows:
  \[
    \begin{bmatrix}
  -1 & -1 & -1 & 1 & 1 & a \\
  1 & 1 & 1 & -1 & -1 & -a \\
  b & 1 & -1 & 1 & -1 & -1 \\
  -b & -1 & 1 & -1 & 1 & 1 \\
  \end{bmatrix}
  \] with $a, b \in [-1,1]$.
  One can verify that we cannot obtain a matrix of rank $1$, regardless of the choice of $a$ and $b$.
  Plugging in this solution set into the larger matrix yields
  \[
  \begin{bmatrix}
  {\color{red} -1} & {\color{red} -1} & {\color{red} -1} & {\color{red} 1} & {\color{red} 1} & {\color{red} a} & -1 & \cdot & \cdot & \cdot \\
  {\color{red} 1} & {\color{red} 1} & {\color{red} 1} & {\color{red} -1} & {\color{red} -1} & {\color{red} a} & \cdot & -1 & \cdot & \cdot \\
  {\color{red} b} & {\color{red} 1} & {\color{red} -1} & {\color{red} 1} & {\color{red} -1} & {\color{red} -1} & \cdot & \cdot & -1 & \cdot \\
  {\color{red} -b} & {\color{red} -1} & {\color{red} 1} & {\color{red} -1} & {\color{red} 1} & {\color{red} 1} & \cdot & \cdot & \cdot & -1 \\
  \cdot & \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & 1 & 1\\
  \end{bmatrix}
  \]

  In order for the $5^{th}$ row to be linearly dependent with the first two rows, we must have $r_5 = -r_1$ by the column $c_7$, and $r_5 = r_2$ by column $c_8$, yielding a contradiction.
  Similarly, we cannot establish linear independence with the last two rows because of restrictions imposed by columns $c_9$ and $c_{10}$.
  Therefore, the matrix completion problem given above has no solution of rank 3, and we conclude that $\abstain{1/2}$ is not $2$-embeddable with $n=5$.
\end{proof}
